---
title: "Trie Usage"
author: "Casimir Saternos"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Trie Usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Other Trie Packages
The rtrie package provides a few simple functions to support tries
representing lists of words.  Other R packages on CRAN provide
trie implementations with different characteristics including:

* [triebeard](https://CRAN.R-project.org/package=triebeard)
* [AhoCorasickTrie](https://CRAN.R-project.org/package=AhoCorasickTrie)

Also see various packages related to trees in general.

# Trie Creation
A list of words can be created programatically or read from a 
data file or other source.  

```{r}
  words<-read.delim(
    file=system.file("extdata", "dictionary.txt", package = "rtrie"), 
    header=F, sep = " ",
    stringsAsFactors = FALSE)
  class(words)
```

In this case a data frame was created from a file. Creating a trie involves a simple function call to the char_tree function.  A trie is created from a vector passed as an argument 
(in this case column V1 from the data frame).  

```{r, eval=FALSE}
trie <- char_tree(words$V1, 'X')
```

To get an idea of the performance, the file in question 
contained `r length(words$V1)` words.  The microbenchmark 
library can be used for timing.

```{r}
  library(rtrie)
  library(microbenchmark)
  timings <- microbenchmark(
    trie <- char_tree(words$V1, 'X'), 
    times=1
  )
  
  print(paste(timings$time / 1000000000, 'seconds'))
```

# Match the Beginning of Words
What are words that start with "stu".
```{r}
cat(matching_words('stu',trie))
```

# Test if a Character String is a Word
Is "stunt" a word?
```{r}
cat(is_word('stunt',trie))
```

How about "stu"?
```{r}
cat(is_word('stu',trie))
```



